Security Audit of Safeplug ``Tor in a Box''

### 2014-03-06 w2sp/report.tex
merging

\begin{itemize}
\item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor for outgoing traffic (see Figure \ref{fig:flow}).
\item Despite the use of Privoxy as an ad-blocker, the Safeplug does nothing to prevent users' browsers from collecting both first- and third-party tracking cookies, allowing users to be de-anonymized across websites despite the presence of Tor.%\cite{arvindpets}.
\item Safeplug users are vulnerable to a Cross-Site Request Forgery (CSRF) attack that allows an attacker external to their home network to modify the Safeplug settings (including silently turning off the use of Tor).
\item A malicious user within the network can modify the Safeplug settings without notifying any other devices on the network.
\item The Safeplug has a higher web request latency than that of the Tor Browser Bundle.
\end{itemize}

@@

%\begin{table}[!t]
%\renewcommand{\arraystretch}{1.3}
%\caption{The platforms and browsers that the Safeplug settings page provides instructions for.}
%\label{table_example}
%\centering
%	\begin{tabular}{|c|c|}
%	\hline
%		Platform & Browsers \\ \hline
%		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
%		OSX & Safari, Chrome, Firefox \\ \hline
%		iOS	& Safari \\ \hline
%		Android	& Chrome \\ \hline
%	\end{tabular}
%\end{table}

\begin{center}
	\begin{tabular}{|c|c|}
	\hline
		Platform & Browsers \\ \hline
		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
		OSX & Safari, Chrome, Firefox \\ \hline
		iOS	& Safari \\ \hline
		Android	& Chrome \\ \hline
	\end{tabular}
\end{center}

@@

If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.  This could be a problem if users simply decide not to do anything with that setting (i.e. don't change the setting to use the Safeplug as a relay node).  In this case, there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.

@@

Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.  Both of these figures show our IP address in the top right corner; due to the change in IP address we can see that our traffic is being routed through Tor.

@@

>>>>

\begin{itemize}
\item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor for outgoing traffic (see Figure \ref{fig:flow}).
\item Despite the use of Privoxy as an ad-blocker, the Safeplug does nothing to prevent users' browsers from collecting both first- and third-party tracking cookies, allowing users to be de-anonymized across websites despite the presence of Tor~\cite{arvindpets}.
\item Safeplug users are vulnerable to a Cross-Site Request Forgery (CSRF) attack that allows an attacker external to their home network to modify the Safeplug settings (including silently turning off the use of Tor).
\item A malicious user within the network can modify the Safeplug settings without notifying any other devices on the network.
\item The Safeplug has a higher web request latency than that of the Tor Browser Bundle.
\end{itemize}

@@

\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{The platforms and browsers that the Safeplug settings page provides instructions for.}
\label{table_example}
\centering
	\begin{tabular}{|c|c|}
	\hline
		Platform & Browsers \\ \hline
		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
		OSX & Safari, Chrome, Firefox \\ \hline
		iOS	& Safari \\ \hline
		Android	& Chrome \\ \hline
	\end{tabular}
\end{table*}

%\begin{center}
%	\begin{tabular}{|c|c|}
%	\hline
%		Platform & Browsers \\ \hline
%		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
%		OSX & Safari, Chrome, Firefox \\ \hline
%		iOS	& Safari \\ \hline
%		Android	& Chrome \\ \hline
%	\end{tabular}
%\end{center}

@@

The two descriptions are targeting two different audiences: one with much more knowledge about technology and Tor, the other with much less knowledge of these topics.  It is likely that at least one of these audiences will not understand one of the descriptions.  This could be a problem if users simply decide not to do anything with that setting (i.e. don't change the setting to use the Safeplug as a relay node).  In this case, there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.

@@

Figure~\ref{fig:before} shows what a web page looks like before turning Tor and ad-blocking on, while Figure~\ref{fig:after} shows the same website after turning Tor and ad-blocking on.  Both of these figures show our IP address in the top right corner; we can see that our traffic is being routed through Tor due to the change in IP address.

@@

\bibitem{arvindpets} Reisman, Dillon and Englehardt, Steven and Eubank, Christian and Zimmerman, Peter and Narayanan, Arvind.  ``Cookies that give you away: Evaluating the surveillance implications of web tracking.'' \emph{Manuscript}.  2014.
